[Re] Predicting metabolic biomarkers of human inborn errors of metabolism

### 2018-02-20 article/Mondeel_Ogundipe_Westerhoff-2017.tex
Additional explanation of the Figure 3 interval prediction

We note that in early versions of this reproduction we were utilising a
medium that allowed influx of \(-1\) for all medium components, as
opposed to \(-10\) now. It turns out that a setting of \(-1\) does
accurately reproduce the results for Figure 2, but not for Figure 3. For
the CBS IEM the WT interval would correspond to \([-1,-1]\) and would
therefore be a point instead of a wide interval as Shlomi et al. draw
it. We included this simulation in the last cell of the notebook
\emph{Reproduce\_figure\_2\_and\_3\_Shlomi2009.ipynb} This is another
example of the inherent sensitivity of the approach to various settings
in the algorithm.

>>>>

We note that in early versions of this reproduction we were utilising a
medium that allowed influx of \(-1\) for all medium components, as
opposed to \(-10\) now. It turns out that a setting of \(-1\) does
accurately reproduce the results for Figure 2, but not for Figure 3. For
the CBS IEM the WT interval would correspond to \([-1,-1]\) and would
therefore be a point instead of a wide interval as Shlomi et al. draw
it. The reason for this stems from the forced flux \(\epsilon = 1\) in
WT. When the maximum influx of methionine is \(-1\) (as a medium
component) it is also required at a flux of \(-1\) due to the forced
active flux in the WT. When the maximum influx is increased to \(-10\)
the lower bound of the predicted interval increases to \(-10\) but the
upper bound does not because \(\epsilon\) is still equal to \(1\).

We included this simulation in the last cell of the notebook. This is
another example of the inherent sensitivity of the approach to various
settings in the algorithm.
